%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{comment}

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{HENGGANG CUI} % Your name
%\address{1856 Fairhill Rd, Allison Park, PA, 15101} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(651)403-3366 \\ cuihenggang@gmail.com \\ https://cuihenggang.github.io}  % Your phone number and email

\begin{document}

% \vspace{-.2in}

\begin{rSection}{PROFILE}

\vspace{-.2in}
\item[] Engineering Manager with 7 years of experience in the auotonomous driving industry.

\end{rSection}
% \vspace{-.05in}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
\hspace{-1em} Languages/Libraries/Tools & Python, PyTorch, C/C$+$$+$, git, JIRA, LaTex\\
\end{tabular}
\end{rSection}
% \vspace{-.05in}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{WORK EXPERIENCE}

\begin{rSubsection}{\hspace{-1em} Motional, Pittsburgh, PA.}{}{}{}
% \vspace{-0.3em}
\item[] \hspace{-2em} {\bf Principal Engineer Team Lead, Senior Manager} \hfill January, 2021 to \emph{now}
\item I lead Motional's Prediction team.
\item My team owns the behavior prediction and ego trajectory generation models for Motional's self-driving car. The models use transformer and graph attention architectures to predict the other road users' future behaviors as well as generate future ego trajectories.
\item I built the team from scratch into now 16 people, with three TLs and one TLM under me.
\item As a Senior Manager, I set technical directions and coach new leaders in the team.
\end{rSubsection}
% \vspace{-.05in}

\begin{rSubsection}{\hspace{-1em} Uber Advanced Technologies Group, Pittsburgh, PA.}{}{}{}
% \vspace{-0.3em}
\item[] \hspace{-2em} {\bf Senior Software Engineer, Tech Lead} \hfill June, 2017 to January, 2021
\item I worked on the production perception and prediction models for Uber ATG's self-driving car. The models detect objects on the road from sensor inputs (including lidar point clouds, camera images, and radar returns) and predict their future behaviors.
% \item As a tech lead, I led projects in the team and mentored junior engineers.
\item As a tech lead and a pioneer in DL-based behavior prediction, I owned production models and published three first-author papers at IRCA.
% \item Works patented and published at \emph{ICRA '21}, \emph{ICRA '20}, \emph{WACV '20}, \emph{IV '20}, \emph{KDD '20}, and \emph{ICRA '19}.
\end{rSubsection}
\end{rSection}
% \vspace{-.05in}

\begin{rSection}{Education}

\begin{rSubsection}{\hspace{-1em} Carnegie Mellon University, Pittsburgh, PA.}{}{}{}
\vspace{-0.3em}
\item[] \hspace{-2em} Ph.D., Electrical and Computer Engineering (GPA: 3.93) \hfill May, 2017
\item Advisor: Greg Ganger
\item Research Topic: Distributed large-scale machine learning systems
% \item[] \hspace{-2em} Master of Science, Electrical and Computer Engineering \hfill May, 2016
\end{rSubsection}
% \vspace{-.1in}

\begin{rSubsection}{\hspace{-1em} Tsinghua University, Beijing, China}{}{}{}
% \vspace{-0.3em}
\item[] \hspace{-2em} Bachelor of Science, Electronic Information Science and Technology \hfill July 2012
\end{rSubsection}

\end{rSection}
% \vspace{-.05in}

\begin{comment}
\begin{rSection}{PHD THESIS RESEARCH}

\hspace{-1em} \textbf{Thesis}: Exploiting Application Characteristics for Efficient System Support for Large-Scale Machine Learning
% \vspace{-.1in}
\begin{list}{\enskip\textbullet}{\leftmargin=2em}
\item \textbf{Committee}: Greg Ganger, Phil Gibbons, Garth Gibson, Eric Xing, and Derek Murray
% \vspace{-.1in}
\item \textbf{Thesis Subprojects}: As follows:
\end{list}

\begin{rSubsection}{\hspace{-1em} GeePS: Specialized Parameter Server for Deep Learning on GPUs}{}
{Published at EuroSys'16, and open-sourced at https://github.com/cuihenggang/geeps}{}
% \small{
% \vspace{-0.3em}
\item Designed GeePS, a distributed parameter server system for distributed deep learning on GPU machines.
\item Achieved good scalability from single-machine Caffe (13$\times$ more throughput with 16 machines), by overlapping communication with computation.
\item Supported DNNs that cannot fit in GPU memory, by swapping data to/from CPU memory in the background.
% }
\end{rSubsection}
% \vspace{-.1in}

\begin{rSubsection}{\hspace{-1em} IterStore: Efficient Parameter Server for Iterative ML}{}
{Published at SoCC'14 and open-sourced at https://github.com/cuihenggang/iterstore}{}
% \small{
% \vspace{-0.3em}
\item Proposed an efficient parameter server architecture that achieves up to 50$\times$ speedup over the baseline.
% }
\end{rSubsection}
% \vspace{-.1in}
\end{comment}

\begin{comment}
\begin{rSubsection}{\hspace{-1em} MLtuner: Automatic ML tuning}{}
{}{}
\vspace{-0.3em}
\item Designed the MLtuner system that automatically tunes ML task tunables, including learning rate, training batch size, and data staleness bound.
\item Used efficient snapshotting and optimization-guided online trial-and-error, allowing MLtuner to find good tunable settings with little overhead.
\item Experimented with real ML tasks, including deep learning and matrix factorization, showing that MLtuner automatically enables performance within 40--178\% of optimal tunable settings.
\end{rSubsection}
% \vspace{-.1in}
% \pagebreak

% \begin{rSubsection}{\hspace{-1em} Stale Synchronous Parallel (SSP): Trading Data Freshness for Speed}{}
% {Published at NIPS'13 and ATC'14}{}
% \vspace{-0.3em}
% \item Designed a parameter server system that supports SSP, a new consistency model for synchronizing parallel ML workers, with tunable data staleness bound.
% \item Experimented with many real ML applications, exploring the tradeoffs of data freshness and speed.
% \end{rSubsection}
% \vspace{-.1in}

\end{rSection}
% \vspace{-.05in}

\end{comment}

% \begin{rSection}{INTERNSHIP}

% \hspace{-1em} \textbf{HP Labs}, advised by Kimberly Keeton \hfill {May 2014 to Aug 2014}

% \vspace{-.1in}
% \begin{rSubsection}{\hspace{-1em} Aperture: Ingest-Time Transformation for Big Time Series Data}{}
%{Internship project at HP Labs, advised by Kimberly Keeton\\
% {Published at SoCC'15, with patent US20170322987A1}{}
% \vspace{-0.3em}
% \item Designed a database for big time series data analytics with low query latencies.
%\item Experimented with many real use cases (correlation search, IP occurrence query, and anomaly detection), showing query latency reductions by over an order of magnitude, with minimal impact on ingest throughput.
% \end{rSubsection}

% \end{rSection}
% \vspace{-.05in}


\begin{rSection}{SELECTED PATENTS}
    \vspace{-.1in}
    \footnotesize{
    % \begin{bibsection}
        \item
        [1]
            Christopher Hazard, Akshay Bhagat, Balarama Raju Buddharaju, Zhongtao Liu, Yunming Shao, Lu Lu, Sammy Omari, and {\bf Henggang Cui}.
            ``Agent Importance Prediction for Autonomous Driving''.
            \emph{US20230294741A1}.
        \item
        [2]
            Bence Cserna, Juraj Kabzan, Kevin C. Gall, Thomas Kølbæk Jespersen, Gianmarco Alessandro Bernasconi, and {\bf Henggang Cui}.
            ``Methods And Systems For Agent Prioritization''.
            \emph{US20230195129A1}.
        \item
        [3]
            {\bf Henggang Cui}, Junheng Wang, Sai Bhargav Yalamanchi, Mohana Prasad Sathya Moorthy, Fang-Chieh Chou, and Nemanja Djuric.
            ``Systems and Methods for Training Predictive Models for Autonomous Devices''.
            \emph{US20230021034A1}.
        \item
        [4]
            Nemanja Djuric, {\bf Henggang Cui}, Thi Duong Nguyen, Fang-Chieh Chou, Tsung-Han Lin, Jeff Schneider, and David McAllister Bradley.
            ``Motion Prediction for Autonomous Devices''.
            \emph{US20200272160A1}.
        \item
        [5]
            Nemanja Djuric, Vladan Radosavljevic, Thi Duong Nguyen, Tsung-Han Lin, Jeff Schneider, {\bf Henggang Cui}, Fang-Chieh Chou, and Tzu-Kuo Huang.
            ``Object Motion Prediction and Autonomous Vehicle Control''.
            \emph{US20190049970A1}.
        % \item
        % [7]
        %    {\bf Henggang Cui}, Kimberly Keeton, Indrajit Roy, Krishnamurthy Viswanathan, and Haris Volos.
        %     ``Processing a query using transformed raw data''.
        %     \emph{US20170322987A1}.
    }
    \end{rSection}
    \vspace{-.05in}    

\pagebreak

\begin{rSection}{SELECTED PUBLICATIONS}
\vspace{-.1in}
\footnotesize{
% \begin{bibsection}
    \item
    [1]
        Sepideh Afshar*, Nachiket Deo*, Akshay Bhagat, Titas Chakraborty, Yunming Shao, Balarama Raju Buddharaju, Adwait Deshpande, {\bf Henggang Cui}.
        ``PBP: Path-based Trajectory Prediction for Autonomous Driving.'' \\
        In \emph{IEEE International Conference on Robotics and Automation (ICRA)}, 2024.
    \item
    [1]
        {\bf Henggang Cui*}, Hoda Shajari*, Sai Yalamanchi, Nemanja Djuric.
        ``Ellipse Loss for Scene-Compliant Motion Prediction.'' \\
        In \emph{IEEE International Conference on Robotics and Automation (ICRA)}, 2021.
    \item
    [2]
        {\bf Henggang Cui}, Fang-Chieh Chou, Jake Charland, Carlos Vallespi-Gonzalez, Nemanja Djuric.
        ``Uncertainty-Aware Vehicle Orientation Estimation for Joint Detection-Prediction Models.''
        In \emph{IEEE International Conference on Intelligent Transportation (ITSC)}, 2021.
    \item
    [3]
        Nemanja Djuric, {\bf Henggang Cui}, Zhaoen Su, Shangxuan Wu, Huahua Wang, Fang-Chieh Chou, Luisa San Martin, Song Feng, Rui Hu, Yang Xu, Alyssa Dayan, Sidney Zhang, Brian C. Becker, Gregory P. Meyer, Carlos Vallespi-Gonzalez, Carl K. Wellington.
        ``MultiXNet: Multiclass Multistage Multimodal Motion Prediction.''
        In \emph{IEEE Intelligent Transportation Systems (IV)}, 2021.
    \item
    [4]
        Eason Wang*, {\bf Henggang Cui*}, Sai Yalamanchi, Mohana Moorthy, Fang-Chieh Chou, Nemanja Djuric.
        ``Predicting Motion of Vulnerable Road Users using High-Definition Maps and Efficient ConvNets.''
        In \emph{SIGKDD Conference on Knowledge Discovery and Data Mining (KDD)}, 2020.
    \item
    [5]
        Fang-Chieh Chou, Tsung-Han Lin, {\bf Henggang Cui}, Vladan Radosavljevic, Thi Nguyen, Tzu-Kuo Huang, Matthew Niedoba, Jeff Schneider, Nemanja Djuric.
        ``Predicting Motion of Vulnerable Road Users using High-Definition Maps and Efficient ConvNets.''
        In \emph{IEEE Intelligent Transportation Systems (IV)}, 2020.
    \item
    [6]
        {\bf Henggang Cui}, Thi Nguyen, Fang-Chieh Chou, Tsung-Han Lin, Jeff Schneider, David Bradley, Nemanja Djuric.
        ``Deep Kinematic Models for Kinematically Feasible Vehicle Trajectory Predictions.''
        In \emph{IEEE International Conference on Robotics and Automation (ICRA)}, 2020.
    \item
    [7]
        Nemanja Djuric, Vladan Radosavljevic, {\bf Henggang Cui}, Thi Nguyen, Fang-Chieh Chou, Tsung-Han Lin, Jeff Schneider.
        ``Uncertainty-aware Short-term Motion Prediction of Traffic Actors for Autonomous Driving.''
        In \emph{IEEE Winter Conference on Applications of Computer Vision (WACV)}, 2020.
    \item
    [8]
        {\bf Henggang Cui}, Vladan Radosavljevic, Fang-Chieh Chou, Tsung-Han Lin, Thi Nguyen, Tzu-Kuo Huang, Jeff Schneider, Nemanja Djuric.
        ``Multimodal Trajectory Predictions for Autonomous Driving using Deep Convolutional Networks.''
        In \emph{IEEE International Conference on Robotics and Automation (ICRA)}, 2019.
    % \item
    % [8]
    %     Matthew Niedoba, {\bf Henggang Cui}, Kevin Luo, Darshan Hegde, Fang-Chieh Chou, Nemanja Djuric.
    %     ``Improving Movement Prediction of Traffic Actors using Off-road Loss and Bias Mitigation.''
    %     In \emph{NeurIPS Workshop on Machine Learning for Autonomous Driving}, 2019.
    \item
    [9]
        {\bf Henggang Cui}, Hao Zhang, Gregory R. Ganger, Phillip B. Gibbons, and Eric P. Xing.
        ``GeePS: Scalable Deep Learning on Distributed GPUs with a GPU-Specialized Parameter Server.''
        In \emph{ACM European Conference on Computer Systems (EuroSys)}, 2016.
        % \emph{Presented at conference}.
    \item
    [10]
        Aaron Harlap, {\bf Henggang Cui}, Wei Dai, Jinliang Wei, Gregory R. Ganger, Phillip B. Gibbons, Garth A. Gibson, and Eric P. Xing.
        ``Addressing the Straggler Problem for Iterative Convergent Parallel ML.''
        In \emph{ACM Symposium on Cloud Computing (SoCC)}, 2016.
    \item
    [11]
        {\bf Henggang Cui}, Kimberly Keeton, Indrajit Roy, Krishnamurthy Viswanathan, and Gregory R. Ganger.
        ``Using Data Transformations for Low-latency Time Series Analysis.''
        In \emph{ACM Symposium on Cloud Computing (SoCC)}, 2015.
        % \emph{Presented at conference}.
    \item
    [12]
        Jinliang Wei, Wei Dai, Aurick Qiao, Qirong Ho, {\bf Henggang Cui}, Gregory R. Ganger, Phillip B. Gibbons, Garth A. Gibson, Eric P. Xing.
        ``Managed Communication and Consistency for Fast Data-Parallel Iterative Analytics.''
        In \emph{ACM Symposium on Cloud Computing (SoCC)}, 2015.
    \item
    [13]
        {\bf Henggang Cui}, Alexey Tumanov, Jinliang Wei, Lianghong Xu, Wei Dai, Jesse Haber-Kucharsky, Qirong Ho, Gregory R. Ganger, Phillip B. Gibbons, Garth A. Gibson, and Eric P. Xing.
        ``Exploiting Iterative-ness for Parallel ML Computations.''
        In \emph{ACM Symposium on Cloud Computing (SoCC)}, 2014.
        % \emph{Presented at conference}.
    \item
    [14]
        {\bf Henggang Cui}, James Cipar, Qirong Ho, Jin Kyu Kim, Seunghak Lee, Abhimanu Kumar, Jinliang Wei, Wei Dai, Gregory R. Ganger, Phillip B. Gibbons, Garth A. Gibson, and Eric P. Xing.
        ``Exploiting Bounded Staleness to Speed Up Big Data Analytics.''
        In \emph{USENIX Annual Technical Conference (ATC)}, 2014.
        % \emph{Presented at conference}.
    \item
    [15]
        Qirong Ho, James Cipar, {\bf Henggang Cui}, Jin Kyu Kim, Seunghak Lee, Phillip B. Gibbons, Garth A. Gibson, Gregory R. Ganger, and Eric P. Xing.
        ``More Effective Distributed ML via a Stale Synchronous Parallel Parameter Server.''
        In \emph{Neural Information Processing Systems (NIPS)}, 2013.
    % \item
    % [16]
        % {\bf Henggang Cui}, Danielle Rasooly, Moises R. N. Ribeiro, and Leonid Kazovsky.
        % ``Optically Cross-Braced Hypercube: A Reconfigurable Physical Layer for Interconnects and Server-Centric Datacenters.''
        % In \emph{Optical Fiber Communication Conference and Exposition (OFC/NFOEC)}, 2012.
    \item
    [16]
        Dan Li, {\bf Henggang Cui}, Yan Hu, Yong Xia, and Xin Wang.
        ``Scalable Data Center Multicast using Multi-class Bloom Filter.''
        In \emph{19th IEEE International Conference on Network Protocols (ICNP)}, 2011.
}
% \end{bibsection}
\end{rSection}
\vspace{-.05in}


% \begin{rSection}{CONFERENCE TALKS}
% \vspace{-.1in}
    % \item
    % [1]
% GeePS: Scalable Deep Learning on Distributed GPUs with a GPU-Specialized Parameter Server \\
    % In \emph{EuroSys 2016}, London, UK \hfill Apr 2016
    % \item
    % [2]
% Using Data Transformations for Low-latency Time Series Analysis \\
    % In \emph{SoCC 2015}, Kohala Coast, HI \hfill Aug 2015
    % \item
    % [3]
% Exploiting Iterative-ness for Parallel ML Computations \\
    % In \emph{SoCC 2014}, Seattle, WA \hfill Nov 2014
    % \item
    % [4]
% Exploiting Bounded Staleness to Speed Up Big Data Analytics \\
    % In \emph{ATC 2014}, Philadelphia, PA \hfill Jun 2014
    % \item
    % [5]
% LazyTable: Distributed Machine Learning with the Stale Synchronous Parallel Model \\
    % In \emph{SOSP 2013 WIP Talk}, Farmington, PA \hfill Nov 2013
% \vspace{.1in}

% \end{rSection}


\begin{comment}
\begin{rSection}{PROFESSION SERVICES}

\small{

\hspace{-1em} \textbf{Program Committee}: \emph{The Web Conference (WWW) '20, NeurIPS '19 ``Machine Learning for Autonomous Driving'' Workshop, CVPR '19 ``Precognition: Seeing through the Future'' Workshop, ACM Symposium on Cloud Computing '17 and '18, Computing Conference '17}

\hspace{-1em} \textbf{Reviewer}: \emph{IEEE International Conference on Robotics and Automation '19, IEEE Robotics and Automation Letters '19, IEEE Big Data '19, Cluster Computing '19 and '20, IEEE Transactions on Network Science and Engineering '18}

% \hspace{-1em} \textbf{Program Committee}: \emph{The Web Conference (WWW)} \hfill {2020}

% \vspace{-.1in}
% \hspace{-1em} \textbf{Reviewer}: \emph{IEEE International Conference on Robotics and Automation} \hfill {2019}

% \vspace{-.1in}
% \hspace{-1em} \textbf{Reviewer}: \emph{IEEE Robotics and Automation Letters} \hfill {2019}

% \vspace{-.1in}
% \hspace{-1em} \textbf{Program Committee}: \emph{NeurIPS ``Machine Learning for Autonomous Driving'' Workshop} \hfill {2019}

% \vspace{-.1in}
% \hspace{-1em} \textbf{Reviewer}: \emph{Cluster Computing} \hfill {2019}

% \vspace{-.1in}
% \hspace{-1em} \textbf{Program Committee}: \emph{CVPR ``Precognition: Seeing through the Future'' Workshop} \hfill {2019}

% \vspace{-.1in}
% \hspace{-1em} \textbf{Program Committee}: \emph{ACM Symposium on Cloud Computing '17 and '18,' Computing Conference '17}

% \vspace{-.1in}
% \hspace{-1em} \textbf{Reviewer}: \emph{IEEE Transactions on Network Science and Engineering} \hfill {2018}

% \vspace{-.1in}
% \hspace{-1em} \textbf{Program Committee}: \emph{ACM Symposium on Cloud Computing} \hfill {2017}

% \vspace{-.1in}
% \hspace{-1em} \textbf{Program Committee}: \emph{Computing Conference} \hfill {2017}

}

\end{rSection}
\vspace{-.05in}

\end{comment}

% \begin{rSection}{TEACHING EXPERIENCE}

% \hspace{-1em} \textbf{Teaching Assistance}: 15746/18746 Storage Systems \hfill {Spring 2015}

% \vspace{-.1in}
% \hspace{-1em} \textbf{Teaching Assistance}: 15746/18746 Storage Systems \hfill {Fall 2016}

% \end{rSection}
% \vspace{-.05in}

\end{document}
